```{r set}
#| message: false
#| include: false
library(tidyverse)
library(sf)
```

# Data {.unnumbered}

## Site infos

Plots of Manaré (MAN430, MAN441 and MAN431).

## Plot infos

Infos from ONF (Caroline Bedeau [caroline.bedeau\@onf.fr](mailto:caroline.bedeau@onf.fr){.email} pers. com.).

-   MAN430
    -   Control
-   MAN431
    -   Logging March-April 2024
    -   Debusquage \~April 2024
    -   Débardage \~ Dry season 2024
-   MAN441
    -   UP1
    -   LIDAR 2023
    -   Logging October-November 2020
    -   Debusquage February-March 2022
    -   Débardage October 2022
    -   Everything is done including fuelwood

## Lidar infos

Infos from ONF (Caroline Bedeau [caroline.bedeau\@onf.fr](mailto:caroline.bedeau@onf.fr){.email} pers. com.).

-   2013 Pre-logging
    -   Riegl LMS-Q560
    -   Height 500m
    -   Angle +/- 30°
    -   Density \~5 pulses / m² ; non homogeneous (recovery 20 à 30%)
-   2023 IFIHSA
    -   part of post-logging MAN441, pre-logging MAN431
    -   Riegl VQ-780II
    -   Height 1000m
    -   Angle +/- 30°
    -   Density \~12 pulses / m² ; non homogeneous (recovery 81%)
-   2023 ONF
    -   part of post-logging MAN441
    -   Riegl VQ-780II
    -   Height 750m
    -   Angle +/- 30°
    -   Density \~20 pulses / m² ; non homogeneous (recovery 61%)
-   2026 ONF for MAN431 post-logging?

## Spatial data

Data from ONF (Caroline Bedeau [caroline.bedeau\@onf.fr](mailto:caroline.bedeau@onf.fr){.email} pers. com.).

```{r datasp}
#| message: false
#| warning: false
zone <- st_read("data/lidar/ScenarioA_ZoneManare1.gpkg", quiet = TRUE) %>% 
  st_transform(crs = 4326)
lidar <- st_read("data/lidar/Lidar_ONF_postexploitation2023.gpkg", quiet = TRUE) %>% 
  st_transform(crs = 4326)
manare <- st_read("data/lidar/designation_AG_Manare.gpkg", quiet = TRUE) %>% 
   st_transform(crs = 4326)
maweyo <- st_read("data/lidar/designation_AG_Maweyo-Saouaoue.gpkg", quiet = TRUE) %>% 
  st_transform(crs = 4326)
ggplot(manare) +
  geom_sf(size = .01, aes(col = "Angeliques")) +
  geom_sf(data = maweyo, size = .01, aes(col = "Angeliques")) +
  geom_sf(data = zone, fill = NA, aes(col = "Zone Manare 1")) +
  geom_sf(data = lidar, fill = NA, aes(col = "LIDAR 2023")) +
  theme_bw() +
  scale_color_manual(values = c("darkgrey", "red", "blue"))
```
